\documentclass{latex2man}

\begin{Name}{1}{interrobang}{Jesse McClure}{launcher menu}{Interrobang - A tiny launcher menu packing a big bang syntax}

\Prog{Interrobang} - A tiny launcher menu packing a big bang syntax.

\end{Name}

\section{Synopsis}
\Prog{interrobang}
	\oOpt{-h}
	\oOpt{-v}
	\oOptArg{-o}{\SP config-string}
	\oOpt{-}
	\oArg{hushbang}

\section{Description}
\Prog{Interrobang} is a scriptable launcher menu with a customizable shortcut syntax and completion options.

\section{Options}
\begin{description}
\item[\Opt{-h}]
	Print help and exit
\item[\Opt{-v}]
	Print version information and exit
\item[\OptArg{-o}{\SP config-string}]
	Override a setting from the runtime configuration with a full line in quotes with a syntax matching that described below for configuration files
\item[\Opt{-}]
	Read configuration file from the standard input
\item[\Arg{hushbang}]
	TODO
\end{description}

\section{Configuration}
Runtime configuration is read from the following files, in order, stopping at the first file found:
\File{stdin} if \Opt{-} is specified on the command line,
\File{\$XDG_CONFIG_HOME/interrobang/config},
\File{\$HOME/.interrobangrc}.

A template configuration file is distributed as \File{/usr/share/interrobang/config}

Each non-empty non-comment line in a configuration file must start with \Opt{set}, \Opt{bang}, or \Opt{tab}.  Lines starting with a # are ignored as comments.

\subsection{Set}
set \Opt{parameter} = \Arg{setting}

The following parameters can be set:

\begin{description}
\item[\Opt{font}]
	Select a font as either an XLFD font string, or a string that would be matched by font-config (fc-match)
\item[\Opt{geometry}]
	One of \Arg{top}, \Arg{bottom}, or a geometry string as \Arg{W}x\Arg{H}+\Arg{X}+\Arg{Y}.  If \Arg{X} or \Arg{Y} are -1 the bar will be centered in that direction.
\item[\Opt{colors}]
	Provide six #RRGGBB color strings for foreground and background for each of normal text, option listings, and selected options.
\item[\Opt{border}]
	Select a border width in pixels and an #RRGGBB color for the boarder as "Npx #RRGGBB"
\item[\Opt{bangchar}]
	Specify the "bang" character.  ! is the default, : is a common alternative.
\item[\Opt{run_hook}]
	A format string into which the selected command will be placed before running.  This can be used to store a history of commands.  This string should contain one \%s which will be replaced by the selected command.
\item[\Opt{autocomp}]
	Whether commands should be autocompleted.  Select 0 for no autocompletion, or a positive number of characters as the minimum number required from the user before completion options are provided.
\item[\Opt{list}]
	Completion options displayed in bar: true or false.
\item[\Opt{last}]
	Last "word" only in completion options: true or false.
\item[\Opt{margin}]
	Number of pixels for the margin between the displayed completion options and the end of the entered text.  Positive values will left-align the options at this margin, while negative values will right-align the options in the window and use this value as the minimum space between entered text and the first option.
\item[\Opt{shell}]
	Specify an alternative shell for launching commands
\item[\Opt{flags}]
	Specify alternative flags to the shell.  The default -c can be replaced with -ic for an interactive shell which will allow for the use of shell rc-defined aliases.
\end{description}

\subsection{Bang}
bang \Opt{keyword} = \Arg{command-string}

TODO

\subsection{Tab}
tab \Opt{keyword} = \Arg{command-string}

TODO

\section{Author}
Copyright \copyright 2013 Jesse McClure \\
License GPLv3: GNU GPL version 3 \URL{http://gnu.org/licenses/gpl.html} \\
This is free software: you are free to change and redistribute it. \\
There is NO WARRANTY, to the extent permitted by law.

Submit bug reports via github: \\
\URL{http://github/com/TrilbyWhite/interrobang.git}

I would like your feedback.  If you enjoy \Prog{Interrobang} see the bottom of the site below for detauls on submitting comments: \\
\URL{http://mccluresk9.com/software.html}

\LatexManEnd
